---
title: "Hands_on_session_text_mining"
author: "Janet Piñero (janet.pinero@upf.edu)"
date: "Last update: `r format(Sys.time(), '%d %B, %Y')`"      
output:
  html_document:
    toc: true
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Exercise 1

We will work with a set of publications related to breast cancer genetics and drug treatment downloaded from Pubmed. I suggest to use the [easyPubMed R package](https://cran.r-project.org/web/packages/easyPubMed/vignettes/getting_started_with_easyPubMed.html). 
I also suggest to use the tutorial [here](https://www.tidytextmining.com/index.html).


You will prepare in teams a report answering the following questions for the disease that was assigned to your team:  

How many papers were published monthly in the topic? (Choose an appropriate visualization)  


```{r}

```

What are the more frequent words employed in the set of documents?  


```{r}

```

Visualize the network of bigrams of your document set.  


```{r}

```

What are the more common genes  mentioned in the publications? Verify that your results represent the current knowledge. (Hint: you can use the information in databases such as [DisGeNET](https://www.disgenet.org/). 


```{r}

```


Perform a clustering analysis. Is it possible to identify common topics mentioned in the clusters?  


```{r}

```



# session info {.unnumbered}

```{r, results='asis',  echo=FALSE, message=FALSE }
sessionInfo()
```
